\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-07-28 manuscript/main.tex
new file:   manuscript/July26.pdf 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	deleted:    manuscript/July26.pdf 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

According to the Ministry of Housing and Urban-Rural Development in China, the proportion of second-hand housing transactions rose to 37.1\% in 2023, with this trend showing continuous growth. Unlike the primary housing market, where transactions are straightforward, the secondary housing market necessitates sellers having access to buyers, thereby making transaction costs a critical factor for both parties. In this context, real estate brokers play a pivotal role in mitigating these costs. They provide essential market information, negotiation support, and legal assistance, thereby facilitating smoother and more efficient transactions in the real estate market. The involvement of brokers reduces the information asymmetry and transactional frictions that are characteristic of the secondary housing market, thus enhancing market efficiency. With the improvement of China's legal system in the real estate market, the brokerage market is expanding and becoming more prosperous. Especially in the context of China's burgeoning real estate market, brokerage firms are assuming an increasingly important role in facilitating the communications between buyers and sellers \citep{glaeser_real_2017}. Given the heterogeneous and "thin" nature of real estate goods \citep{HAN2015813}, the expertise and local market knowledge of real estate brokers have become indispensable in navigating the complex real estate landscape.

Chinese real estate listings market possesses distinct features characterized by the prominence of offline stores, setting it apart from the markets in other developed countries. Compared to the United States, where the Multiple Listing Service (MLS) provides comprehensive and reliable information online, facilitating transactions in a market where houses are typically situated far apart, the role of offline real estate stores is minimized.\footnote{\citet{hendel_relative_2009} documents that the MLS market experiences a significant growth in recent years.} In contrast, Chinese real estate market is predominantly offline-based, with online listings serving mainly as references. Face-to-face interactions remain crucial for transactions. Additionally, the Chinese government imposes stringent restrictions on the online listing prices, leading to a reluctance among sellers to list their properties online. This regulatory environment allows real estate brokerages to sometimes post misleading prices to attract potential buyers, subsequently offering private information about other properties. Moreover, the Chinese real estate brokerage market operates under a bilateral agency model, resulting in lower transaction efficiency compared to the United States brokerage market. In Singapore, the real estate market is heavily influenced by government-coordinated prices and evaluation companies' suggested prices. Conversely, in China, sellers have more freedom to set arbitrary listing prices. It is common practice for Chinese sellers to list their properties at higher prices, anticipating that buyers will negotiate and feel incentivized by securing a perceived better deal.

Even though the Chinese real estate brokerage market has traditionally been characterized by intense competition among offline stores, the advent of online platforms has dramatically reshaped the dynamics of real estate transactions. Brokerage consolidation, a process where larger firms absorb smaller ones into a unified platform, is emerging as a transformative trend, redefining how properties are bought and sold across China. Lianjia, the largest real estate brokerage in China, has revolutionized real estate transactions through the establishment of the Beke platform. This platform enables rapid expansion by integrating offline stores on a large scale while leveraging the advantages of resource sharing. However, prior to 2018, the platform Beke primarily focused on facilitating listings from Lianjia's offline stores and aimed to attract buyers from the market. However, in 2014, Beke established a new strategy named Agent Cooperate Network (ACN), which integrates and shares the content across its multiple subsidiaries to realize multiple revenue models simultaneously.\footnote{The ACN model disaggregates the transaction process into specialized tasks handled by individual agents or stores. These tasks include seller-side activities such as sourcing sellers, maintaining property listings, commission negotiations, and buyer-side activities like client acquisition, property-client matching, transaction facilitation, and financial services assistance.} Moreover, in 2018, Lianjia decided to enhance its Agent Cooperation Network (ACN) strategy by incorporating smaller brokerages into its network and launching franchise stores under the brand name Deyou, along with other smaller formats. This strategic move aimed to increase network effects and further consolidate the platform, thereby enhancing market power and operational efficiency.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\textwidth]{../figures/distribution_of_cities_share.pdf}
  \caption{Distribution of Lianjia's stores' percentage across China}
  \label{fig:precise_proportion_contraction}
  Note: This plot displays the percentage of Lianjia's offline stores in each city relative to the total number of brokerages in that city, based on data from AutoNavi Map. Gray areas indicate invalid information, while white areas denote cities without any Lianjia stores. Additionally, Sansha city is featured in the bottom right corner of the graph.
\end{figure}

@@

According to Lianjia's IPO prospectus, the company is projected to achieve approximately 76\% of cross-store transactions in 2021. This underscores the necessity of analyzing the network effects among Lianjia's offline stores and conducting a detailed examination of these effects. To assess Lianjia's network effect, we propose a measure of the local network effect by incorporating neighborhoods and offline stores, given that offline stores predominantly cluster around neighborhoods. We employ a Breadth-First Search (BFS) algorithm to construct the network formation and propose a gravity-based measure to evaluate the offline clustered network effect on neighborhoods. Additionally, we examine the impact of online-mediated consolidation on the offline stores' network effect on neighborhoods. Our findings reveal that Lianjia's offline stores exhibit a moderate network effect characterized by local clustering patterns.\footnote{\ref{fig:typical_sample_lianjia} shows a typical observation in Chengdu that two proximate Lianjia stores closely cooperate to manage property listings. In this arrangement, agents have the flexibility to bring customers for house tours.} Furthermore, the platform-mediated consolidation significantly enhances the network effect, indicating that this consolidation strategy effectively strengthens the network effect of Lianjia's offline stores. Lastly, the result also confirms that the clustering within a small segmented market allows the company to coexist with competitors, with the large company satisfying the majority of customers while other firms cater to heterogeneous customer needs. Lianjia does not exclude other brokerages from the market, but rather coexists with them, thereby enhancing the overall market competitiveness. This finding is consistent with the study by \citep{gilbukh_goldsmith-pinkham_2019}, which indicates that inexperienced intermediaries hold a large market share, but their transaction efficiency is lower compared to experienced intermediaries.

@@

The literature on the real estate market, particularly the role of real estate brokerages, is extensive and informative, starting with the foundational work of \citep{Rosen_hedonic} who introduced the hedonic pricing model. This model breaks down property prices by analyzing internal and external factors. However, it's worth noting that this model does not adequately account for market asymmetries and information disparities, leading to potential inaccuracies in pricing. A fundamental study by \citep{Akerlof_1970} highlights the significant impact of asymmetric information on market dynamics, using the market for used cars as an example. Here, the prevalence of low-quality goods, known as 'lemons', often leads to market inefficiencies, a problem that is mirrored in the real estate sector. The challenge of asymmetric information in real markets was further emphasized by \citet{grossman_impossibility_1980}, who questioned the feasibility of the effective market assumption, particularly under conditions of information disparity.

@@

The strategic behavior of real estate brokerages has been documented to leverage informational advantages. \citet{AGARWAL2019715} confirms that brokerages, as market intermediaries, possess nuanced knowledge of market conditions, enabling them to negotiate discounts effectively. Furthermore, \citet{HAN2015813} discusses the varying bargaining power of brokerages across unidirectional and bidirectional markets, influencing their operational strategies. This is corroborated by evidence suggesting that properties listed with lower commission rates not only sell less frequently but also take longer to sell \citep{10.1257/app.20160214}. Additionally, studies have documented that brokerages may adopt discriminatory strategies, steering minorities into neighborhoods with lower economic opportunities and higher exposures to crime and pollution, thereby contributing to persistent social and economic inequalities in the United States \citep{RePEc:ucp:jpolec:doi:10.1086/720140}. The advent of online platforms has significantly altered the landscape of real estate transactions. \citet{ZUMPANO2003134} notes that while the duration of property searches has not changed markedly, the scope of searches has broadened to encompass more online listings. Moreover, \citet{ZHANG2021101104} associates the rise of online platforms with a reduction in existing home prices and an increase in sales volumes, a dynamic influenced by factors such as new home prices and household demographics. However, a detailed analysis of the impact of the presence of these platforms on market performance of offline stores remains scant.

@@

To our knowledge, this paper represents the pioneering empirical investigation into the effects of offline store expansion and platform-mediated consolidation within the real estate brokerage market. Furthermore, it is the first to analyze the local network effects within the specific context of real estate transactions. Additionally, this paper systematically examines how informational advantages can enhance brokerage revenue within the framework of local network effects. By delving into these dynamics, we aim to contribute to the broader economics literature by providing a nuanced understanding of how offline and online integration influences market behavior and outcomes. Our findings offer meaningful insights into the strategic decisions of real estate brokerages, highlighting the significance of network effects and informational advantages in shaping competitive advantage and market performance. This research not only fills critical gaps in the literature but also provides a comprehensive framework for future studies to explore the intersection of offline expansion, digital consolidation, and local network effects in various economic contexts. By systematically examining these phenomena, we enhance the understanding of how technological and infrastructural developments can drive revenue generation and market consolidation in the real estate industry and beyond.

@@

Each type of POI, excluding brokerages offline stores information, was matched to our data within a 500-meter radius, a distance typically covered by walking and consistent with urban planning standards for accessible urban design. This radius reflects the immediate urban environment influencing residential desirability and property values, as most of these POIs provide recreational services. Additionally, geo-informational data, including annual GDP data from \citet{zhao_forecasting_2017}, nighttime lights data from \citet{elvidge_annual_2021}, and air pollution data from \citet{doi:10.1021/acs.est.1c05309}, was integrated into our research. The centroid of the neighborhood-level data's polygon was generated, and values from the geo-informational data were extracted. By merging these data sources with our research panel, a comprehensive research sample was constructed.

@@

From Figure \ref{fig:RD_design} we can see that there is indeed discontinuity in 410 meters of communities to the nearest Lianjia's store, which is pretty close to the lianjia's 5-minute walk distance policy (approximately 410 meters). The observed decline in the Lianjia's influence is marked and suggests a pronounced reduction in its impact on the system overall within our study sample. This phenomenon can be attributed to the implementation of the Lianjia's proximity to customers policy, which is evidenced at the data level. Table \ref{tab:rd_bandwidth_kernel_results} considers different kernel and bandwidth choices, and the results are consistent with the 410 meters radius. The results are robust to different bandwidth and kernel choices, which suggests that the 410 meters is the optimal radius for Lianjia's offline stores.\footnote{It is important to note that we should avoid using bandwidths that correspond to distances too small relative to the proximity between Lianjia stores and neighborhoods. This is because our evaluation of neighborhood proximity is based on the centroid of each neighborhood. The distance from a store to the centroid does not necessarily imply that the store is not close to the neighborhood itself. Therefore, when distances are very close to the neighborhood centroid, it is reasonable to consider the store as approximately close to the neighborhood as well.} To check the robustness of the results, we conducted a series of robustness checks. The results are shown in Appendix \ref{sec:additional_rdd}.

@@

One another common concern in RDD is the potential for manipulation around the cutoff, which could invalidate the results. To address this, a "Donut Hole" robustness check can be implemented, where observations close to the cutoff are excluded to ensure that the results are not driven by manipulation or other local irregularities. In this study, we apply a Donut Hole robustness check to an RDD with a cutoff of 410 meters. Specifically, we sequentially exclude observations within certain distances from the cutoff and re-estimate the treatment effect. The distances considered for exclusion are 5, 7.5, 10, 12.5, 15, 17.5, 20 meters, and they are correspondingly dropping 7.85\%, 11.73\%, 15.59\%, 19.48\%, 23.66\%, 27.88\% and 31.71\% of our effective estimation data, respectively. Appendix Table \ref{tab:rd_robust_results} indicate that up to the exclusion of 20\% of the estimated data, the treatment effect estimates remain consistent and robust, thereby demonstrating the robustness of the estimated treatment effects to the exclusion of data points near the cutoff. Moreover, we find that adding control variables may help us to better estimate the treatment effect and make our model more robust.

@@

After constructing our optimal radius, we recalcualte the number of lianjia and other brokerages' stores within this radius. To check the robustness of the data, we divide our data to those with lianjia and those without lianjia and to check whether lianjia's offline stores have influential effect on the transaction effect in the neighborhoods. We can see that for transaction numbers, income, number of house tours and price concession are all significantly different in those neighborhoods with or without lianjia. In addition, we find that the other brokerages also have the same tendency that they typically open stores with the same strategy as Lianjia, which suggests that Lianjia does not have the market power to exclude competent companies from entering the market, and it also suggests that the market is not monopolized by Lianjia. We plot the relationship between the number of other brokerages's stores and the number of lianjia's stores and the figure is shown in Figure \ref{fig:same_distribution}. The figure shows that the the number of other brokerages' stores is positively correlated and the general trend tends to be linear, which further suggests that the market is not monopolized by Lianjia.

From Table \ref{tab:statistical_district} we can see that the in our metro areas, the neighborhoods with lianjia within the influential radius tends to have higher number of sales, and the final transaction price is also \textyen 910,000 (approximately 35\%) higher than those neighborhoods without lianjia. Moreover, the number of other stores within the influential distance is also signnificantly more than 7.3, which also aligns with our previous intuition that the market is not monopolized by Lianjia. This significance difference suggests that if we treat our sample as a cross sectional data and estimate the result with static model without considering the individual fixed effect, we may get a biased result. Besides, our model may suffer from endogeneity issue, since the number of lianjia's stores may be endogenous to the transaction price and the number of stores.

@@

    Note that the code book of the variables can be seen in the Appendix \ref{tab:codebook} and with or without lianjia represent whether there are Lianjia's offline stores within the influential radius.
    \end{tiny}
\end{table}

@@

  Note that the code book of the variables can be seen in the Appendix \ref{tab:codebook} and with or without lianjia represent whether there are Lianjia's offline stores within the influential radius.
  \end{tiny}  
\end{table}

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{../figures/scatter_plot_with_two_brokerages.pdf}
    \caption{Tendency between two types of brokerages}
    \label{fig:same_distribution}
    Note: the x-axis is the number of lianjia's stores and the y-axis is the number of other brokerages' stores. The fit is a cubic polynomial fit.
\end{figure}

@@

In our analysis, we focus on several dependent variables: \emph{the natural logarithm of lianjia's transaction number}, \emph{the natural logarithm of home tours}, \emph{the natural logarithm of transaction period} and \emph{the price concession}. To take the natural logarithm without lossing information, we decided to add one to the number of house tours because some transactions are purely online-based. Additionally, we decided to winsorize the sample for the natural logarithms of Lianjia's transaction number, home tours, and transaction period at the 1st and 99th percentiles to mitigate the influence of extreme values. The price concession is defined as $|\frac{\text{transaction price} - \text{listing price}}{\text{listing price}}| \times 100\%$. To quantify Lianjia's impact, we begin by establishing a key stylized fact, which we develop a Density-Based Index (DBI) index to capture the Lianjia's offline stores' influential ratio. The index is to measure the effects of Lianjia's operations and its continuous expansion. The definition of this index is informed by the results of an influential radius test, which helps us capture the spatial extent of Lianjia's influence on local real estate markets. This approach allows for a more nuanced understanding of how Lianjia's presence affects key market variables. The DBI is calculated as follows:

@@

    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual}. In column 1 and 2, we estimated the model using the neighborhood-level data and in column 3 and 4, we estiamted the model using the individual-level data, respectively. 
    \label{tab:stylized_fact}
    \end{scriptsize}
\end{table}

@@

@@

In the preceding section, our research concentrated on evaluating the dynamic impact of Lianjia's offline store operations. Nevertheless, the presence of a self-selection bias in this dynamic entry factor necessitates the application of causal inference methods to better estimate the effect of Lianjia's offline stores. Consequently, we adopted the Difference-in-Difference (DID) estimation to estimate the offline's store's entry's influence on the market performance. From the market's performance, the Lianjia's offline's store's entry into the segmented market is an exogenous shock to the two-sided customers, where sellers are more likey to be attracted by the brokerage and buyers are also more likely to be attracted by the more listing information in the neighborhood. Although Lianjia's entry is not a randomized event, the DiD estimation method remains consistent in estimating the entry effect by comparing variations in outcome variables before and after Lianjia's entry in the segmented market.

@@

This weight represents the strength of the connection between the stores, enabling us to construct a network graph for our analysis. To visualize this network, we randomly selected 10 points and used a maximum search depth of 10 to plot the graph, as shown in Figure \ref{fig:network_formation_effect_graph}. WE constructed the measure indices as local clustering effect and global clustering effect. The local clustering effect refers to the degree to which nodes in a network tend to cluster together, forming tight-knit groups. In contrast, the global clustering effect shows the overall pattern of clustering across the entire network. Detailed indices for each city and each year is reported in Table \ref{tab:local_global_clustering_indices}. In this graph, the size of the nodes indicates the significance of the local clustering effect, with larger nodes representing stronger local clustering.

@@

@@

@@

@@

\bibitem[Piazzesi et al.(2020)]{piazzesi_segmented_2020}
Piazzesi, M., M. Schneider, and J. Stroebel. 2020. Segmented Housing Search. \textit{American Economic Review}, 110(3), 720-759.

>>>>

According to the Ministry of Housing and Urban-Rural Development in China, the proportion of second-hand housing transactions rose to 37.1\% in 2023, with this trend showing continuous growth. Unlike the primary housing market, where transactions are straightforward, the secondary housing market necessitates sellers having access to buyers, thereby making transaction costs a critical factor for both parties. In this context, real estate brokers play a pivotal role in mitigating these costs. They provide essential market information, negotiation support, and legal assistance, thereby facilitating smoother and more efficient transactions in the real estate market. The involvement of brokers reduces the information asymmetry and transactional frictions that are characteristic of the secondary housing market, thus enhancing market efficiency.

With the improvement of China's legal system in the real estate market, the brokerage market is expanding and becoming more prosperous. Moreover, it is not merely a matter of legal improvement, as in the past, the intermediary market was quite chaotic, with individuals being able to set up a brokerage business without any qualifications. Nowadays, the government has taken steps to regulate the disorderly conduct of intermediaries through administrative and legal measures, leading to a more standardized and orderly market environment. Especially in the context of China's burgeoning real estate market, brokerage firms are assuming an increasingly important role in facilitating the communications between buyers and sellers \citep{glaeser_real_2017}. Given the heterogeneous and "thin" nature of real estate goods \citep{HAN2015813}, the expertise and local market knowledge of real estate brokers have become indispensable in navigating the complex real estate landscape.

The listing service of Chinese real estate market possesses distinct features characterized by the prominence of offline stores, setting it apart from the markets in other developed countries. Compared to the United States, where the Multiple Listing Service (MLS) provides comprehensive and reliable information online, facilitating transactions in a market where suits are typically situated far apart, the role of offline real estate stores is minimized.\footnote{\citet{hendel_relative_2009} documents that the MLS market experiences a significant growth in recent years.} In contrast, Chinese real estate market is predominantly offline-based, with online listings serving mainly as references. Face-to-face interactions remain crucial for transactions. Additionally, Chinese government imposes stringent restrictions on the upper and lower limits of online listing prices, leading to a reluctance among sellers to list their properties online. This regulatory environment allows real estate brokerages to sometimes post misleading prices to attract potential buyers, subsequently offering private information about other properties. Moreover, the Chinese real estate brokerage market operates under a bilateral agency model, resulting in lower transaction efficiency compared to the United States brokerage market. In Singapore, the real estate market is heavily influenced by government-coordinated prices and evaluation companies' suggested prices. Conversely, in China, sellers have more freedom to set arbitrary listing prices in the offline market. It is common practice for Chinese sellers to list their properties at higher prices, anticipating that buyers will negotiate and feel incentivized by securing a perceived better deal.

Even though the Chinese real estate brokerage market has traditionally been characterized by intense competition among offline stores, the advent of online platforms has dramatically reshaped the dynamics of real estate transactions. Brokerage consolidation, a process where larger firms absorb smaller ones into a unified platform, is emerging as a transformative trend, redefining how properties are bought and sold across China. Lianjia, the largest real estate brokerage in China, has revolutionized real estate transactions through the establishment of the Beke platform. This platform enables rapid expansion by integrating offline stores on a large scale while leveraging the advantages of resource sharing. However, prior to 2018, the platform Beke primarily focused on facilitating listings from Lianjia's offline stores and aimed to attract buyers from the market. In 2014, Beke introduced a strategic initiative called the Agent Cooperation Network (ACN), which aims to integrate and share resources across its various subsidiaries. This strategy enables the realization of multiple revenue streams simultaneously, thereby optimizing operational efficiency and enhancing overall economic performance.\footnote{The ACN model disaggregates the transaction process into specialized tasks handled by individual agents or stores. These tasks include seller-side activities such as sourcing sellers, maintaining property listings, commission negotiations, and buyer-side activities like client acquisition, property-client matching, transaction facilitation, and financial services assistance.} Moreover, in 2018, Lianjia decided to enhance its Agent Cooperation Network (ACN) strategy by incorporating smaller brokerages into its network and launching franchise stores under the brand name Deyou, along with other smaller formats. This strategic move aimed to increase network effects and further consolidate the platform, thereby enhancing market power and operational efficiency.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\textwidth]{../figures/distribution_of_cities_share.pdf}
  \caption{Distribution of Lianjia's stores' percentage across China}
  \label{fig:precise_proportion_contraction}
  Note: This plot displays the percentage of Lianjia's offline stores in each city relative to the total number of brokerages in that city, based on data from AutoNavi Map. Gray areas indicate invalid information, while white areas denote cities without any Lianjia stores. Additionally, Sansha city is featured in the bottom right corner of the graph. The base map is sourced from the AutoNavi Map.
\end{figure}

@@

According to Lianjia's IPO prospectus, the company is projected to achieve approximately 76\% of cross-store transactions in 2021. This underscores the necessity of analyzing the network effects among Lianjia's offline stores and conducting a detailed examination of these effects. To assess Lianjia's network effect, we propose a measure of the local network effect by incorporating neighborhoods and offline stores, given that offline stores predominantly cluster around neighborhoods. We employ a Breadth-First Search (BFS) algorithm to construct the network formation and propose a gravity-based measure to evaluate the offline clustered network effect on neighborhoods. Additionally, we examine the impact of online-mediated consolidation on the offline stores' network effect on neighborhoods. Our findings reveal that Lianjia's offline stores exhibit a moderate network effect characterized by local clustering patterns.\footnote{\ref{fig:typical_sample_lianjia} shows a typical observation in Chengdu that two proximate Lianjia stores closely cooperate to manage property listings. In this arrangement, agents have the flexibility to bring customers for house tours.} Furthermore, the platform-mediated consolidation significantly enhances the network effect, indicating that this consolidation strategy effectively strengthens the network effect of Lianjia's offline stores. Lastly, the result also confirms that the clustering within a small segmented market allows the company to coexist with competitors, with the large company satisfying the majority of customers while other firms cater to heterogeneous customer needs. Lianjia does not exclude other brokerages from the market, but rather coexists with them, thereby enhancing the overall market competitiveness.\footnote{This finding is consistent with the study by \citep{gilbukh_goldsmith-pinkham_2019}, which indicates that inexperienced intermediaries hold a large market share, but their transaction efficiency is lower compared to experienced intermediaries.}

@@

The literature on the real estate market, particularly the role of real estate brokerages, is extensive and informative, starting with the foundational work of \citep{Rosen_hedonic} who introduced the hedonic pricing model. This model breaks down property prices by analyzing internal and external factors. However, it's worth noting that this model does not adequately account for market asymmetries and information disparities, leading to potential inaccuracies in pricing. A fundamental study by \citep{Akerlof_1970} highlights the significant impact of asymmetric information on market dynamics, using the market for used cars as an example. Here, the prevalence of low-quality goods, known as `lemons', often leads to market inefficiencies, a problem that is mirrored in the real estate sector. The challenge of asymmetric information in real markets was further emphasized by \citet{grossman_impossibility_1980}, who questioned the feasibility of the effective market assumption, particularly under conditions of information disparity.

@@

The strategic behavior of real estate brokerages has been documented to leverage informational advantages. \citet{AGARWAL2019715} confirms that brokerages, as market intermediaries, possess nuanced knowledge of market conditions, enabling them to negotiate discounts effectively. Furthermore, \citet{HAN2015813} discusses the varying bargaining power of brokerages across unidirectional and bidirectional markets, influencing their operational strategies. This is corroborated by evidence suggesting that properties listed with lower commission rates not only sell less frequently but also take longer to sell \citep{10.1257/app.20160214}. Additionally, studies have documented that brokerages may adopt discriminatory strategies, steering minorities into neighborhoods with lower economic opportunities and higher exposures to crime and pollution, thereby contributing to persistent social and economic inequalities in the United States \citep{RePEc:ucp:jpolec:doi:10.1086/720140}. The advent of online platforms has significantly altered the landscape of real estate transactions. \citet{ZUMPANO2003134} notes that while the duration of property searches has not changed markedly, the scope of searches has broadened to encompass more online listings. Moreover, \citet{ZHANG2021101104} associates the rise of online platforms with a reduction in existing house prices and an increase in sales volumes, a dynamic influenced by factors such as new house prices and household demographics. However, a detailed analysis of the impact of the presence of these platforms on market performance of offline stores remains scant.

@@

Based on the study of existing literature, this paper represents the pioneering empirical investigation into the effects of offline store expansion and platform-mediated consolidation within the real estate brokerage market. Furthermore, it is the first to analyze the local network effects within the specific context of real estate transactions. Additionally, this paper systematically examines how informational advantages can enhance brokerage revenue within the framework of local network effects. By delving into these dynamics, we aim to contribute to the broader economics literature by providing a nuanced understanding of how offline and online integration influences market behavior and outcomes. Our findings offer meaningful insights into the strategic decisions of real estate brokerages, highlighting the significance of network effects and informational advantages in shaping competitive advantage and market performance. This research not only fills critical gaps in the literature but also provides a comprehensive framework for future studies to explore the intersection of offline expansion, digital consolidation, and local network effects in various economic contexts. By systematically examining these phenomena, we enhance the understanding of how technological and infrastructural developments can drive revenue generation and market consolidation in the real estate industry and beyond.

@@

Each type of POI, excluding brokerages offline stores information, was matched to our data within a 500-meter radius, a distance typically covered by walking and consistent with urban planning standards for accessible urban design.\footnote{We chose a 500-meter radius because the existing literature does not specifically document whether these types of points of interest (POIs) adhere strictly to the 5-minute walk policy. Furthermore, several studies have utilized a 500-meter radius to examine the influence of various types of POIs, including: \citep{LI2019165, doi:10.1287/mnsc.2019.3550}} This radius reflects the immediate urban environment influencing residential desirability and property values, as most of these POIs provide recreational services. Additionally, geo-informational data, including annual GDP data from \citet{zhao_forecasting_2017}, nighttime lights data from \citet{elvidge_annual_2021}, and air pollution data from \citet{doi:10.1021/acs.est.1c05309}, was integrated into our research. The centroid of the neighborhood-level data's polygon was generated, and values from the geo-informational data were extracted. By merging these data sources with our research panel, a comprehensive research sample was constructed.

@@

From Figure \ref{fig:RD_design} we can see that there is indeed discontinuity in 410 meters of communities to the nearest Lianjia's store, which is pretty close to the Lianjia's 5-minute walk distance policy (approximately 410 meters). The observed decline in the Lianjia's influence is marked and suggests a pronounced reduction in its impact on the system overall within our study sample. This phenomenon can be attributed to the implementation of the Lianjia's proximity to customers policy, which is evidenced at the data level. Table \ref{tab:rd_bandwidth_kernel_results} considers different kernel and bandwidth choices, and the results are consistent with the 410 meters radius. The results are robust to different bandwidth and kernel choices, which suggests that the 410 meters is the optimal radius for Lianjia's offline stores.\footnote{It is important to note that we should avoid using bandwidths that correspond to distances too small relative to the proximity between Lianjia stores and neighborhoods. This is because our evaluation of neighborhood proximity is based on the centroid of each neighborhood. The distance from a store to the centroid does not necessarily imply that the store is not close to the neighborhood itself. Therefore, when distances are very close to the neighborhood centroid, it is reasonable to consider the store as approximately close to the neighborhood as well.} To check the robustness of the results, we conducted a series of robustness checks. The results are shown in Appendix \ref{sec:additional_rdd}.

@@

One another common concern in RDD is the potential for manipulation around the cutoff, which could invalidate the results. To address this, a ``Donut Hole" robustness check can be implemented, where observations close to the cutoff are excluded to ensure that the results are not driven by manipulation or other local irregularities. In this study, we apply a Donut Hole robustness check to an RDD with a cutoff of 410 meters. Specifically, we sequentially exclude observations within certain distances from the cutoff and re-estimate the treatment effect. The distances considered for exclusion are 5, 7.5, 10, 12.5, 15, 17.5, 20 meters, and they are correspondingly dropping 7.85\%, 11.73\%, 15.59\%, 19.48\%, 23.66\%, 27.88\% and 31.71\% of our effective estimation data, respectively. Appendix Table \ref{tab:rd_robust_results} indicate that up to the exclusion of 20\% of the estimated data, the treatment effect estimates remain consistent and robust, thereby demonstrating the robustness of the estimated treatment effects to the exclusion of data points near the cutoff. Moreover, we find that adding control variables may help us to better estimate the treatment effect and make our model more robust.

@@

After constructing our optimal radius, we recalcualte the number of Lianjia and other brokerages' stores within this radius. To check the robustness of the data, we divide our data to those with Lianjia and those without Lianjia and to check whether Lianjia's offline stores have influential effect on the transaction effect in the neighborhoods. We can see that for transaction numbers, income, number of house tours and price concession are all significantly different in those neighborhoods with or without Lianjia. In addition, we find that the other brokerages also have the same tendency that they typically open stores with the same strategy as Lianjia, which suggests that Lianjia does not have the market power to exclude competent companies from entering the market, and it also suggests that the market is not monopolized by Lianjia. We plot the relationship between the number of other brokerages's stores and the number of Lianjia's stores and the figure is shown in Figure \ref{fig:same_distribution}. The figure shows that the the number of other brokerages' stores is positively correlated and the general trend tends to be linear, which further suggests that the market is not monopolized by Lianjia.

From Table \ref{tab:statistical_district} we can see that the in our metro areas, the neighborhoods with Lianjia within the influential radius tends to have higher number of sales, and the final transaction price is also \textyen 910,000 (approximately 35\%) higher than those neighborhoods without Lianjia. Moreover, the number of other stores within the influential distance is also signnificantly more than 7.3, which also aligns with our previous intuition that the market is not monopolized by Lianjia. This significance difference suggests that if we treat our sample as a cross sectional data and estimate the result with static model without considering the individual fixed effect, we may get a biased result. Besides, our model may suffer from endogeneity issue, since the number of Lianjia's stores may be endogenous to the transaction price and the number of stores.

@@

    Note that the code book of the variables can be seen in the Appendix \ref{tab:codebook} and with or without Lianjia represent whether there are Lianjia's offline stores within the influential radius.
    \end{tiny}
\end{table}

@@

  Note that the code book of the variables can be seen in the Appendix \ref{tab:codebook} and with or without Lianjia represent whether there are Lianjia's offline stores within the influential radius.
  \end{tiny}  
\end{table}

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{../figures/scatter_plot_with_two_brokerages.pdf}
    \caption{Tendency between two types of brokerages}
    \label{fig:same_distribution}
    Note: the x-axis is the number of Lianjia's stores and the y-axis is the number of other brokerages' stores. The fit is a cubic polynomial fit.
\end{figure}

@@

In our analysis, we focus on several dependent variables: \emph{the natural logarithm of Lianjia's transaction number}, \emph{the natural logarithm of home tours}, \emph{the natural logarithm of transaction period} and \emph{the price concession}. To take the natural logarithm without lossing information, we decided to add one to the number of house tours because some transactions are purely online-based. Additionally, we decided to winsorize the sample for the natural logarithms of Lianjia's transaction number, home tours, and transaction period at the 1st and 99th percentiles to mitigate the influence of extreme values. The price concession is defined as $|\frac{\text{transaction price} - \text{listing price}}{\text{listing price}}| \times 100\%$. To quantify Lianjia's impact, we begin by establishing a key stylized fact, which we develop a Density-Based Index (DBI) index to capture the Lianjia's offline stores' influential ratio. The index is to measure the effects of Lianjia's operations and its continuous expansion. The definition of this index is informed by the results of an influential radius test, which helps us capture the spatial extent of Lianjia's influence on local real estate markets. This approach allows for a more nuanced understanding of how Lianjia's presence affects key market variables. The DBI is calculated as follows:

@@

    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual}. In column 1 and 2, we estimated the model using the neighborhood-level data and in column 3 and 4, we estiamted the model using the individual-level data, respectively. Standard Errors are clustered at the business area level.
    \label{tab:stylized_fact}
    \end{scriptsize}
\end{table}

@@

    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual}. Standard Errors are clustered at the business area level.
    \end{scriptsize}
  \end{center}
\end{table}

@@

In the preceding section, our research concentrated on evaluating the dynamic impact of Lianjia's offline store operations. Nevertheless, the presence of a self-selection bias in this dynamic entry factor necessitates the application of causal inference methods to better estimate the effect of Lianjia's offline stores. Consequently, we adopted the Difference-in-Difference (DID) estimation to estimate the offline's store's entry's influence on the market performance. From the market's performance, the Lianjia's offline's store's entry into the segmented market is an exogenous shock to the two-sided customers, where sellers are more likey to be attracted by the brokerage and buyers are also more likely to be attracted by the more listing information in the neighborhood. Although Lianjia's entry is not a randomized event, the DID estimation method remains consistent in estimating the entry effect by comparing variations in outcome variables before and after Lianjia's entry in the segmented market.

@@

This weight represents the strength of the connection between the stores, enabling us to construct a network graph for our analysis. To visualize this network, we randomly selected 10 points and used a maximum search depth of 10 to plot the graph, as shown in Figure \ref{fig:network_formation_effect_graph}. We constructed the measure indices as local clustering effect and global clustering effect. The local clustering effect refers to the degree to which nodes in a network tend to cluster together, forming tight-knit groups. In contrast, the global clustering effect shows the overall pattern of clustering across the entire network. Detailed indices for each city and each year is reported in Table \ref{tab:local_global_clustering_indices}. In this graph, the size of the nodes indicates the significance of the local clustering effect, with larger nodes representing stronger local clustering.

@@

    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual}. Robsut Standard Errors are reported in parentheses.
    \end{scriptsize}
  \end{center}
\end{table}

@@

\bibitem[Chu et al.(2021)]{doi:10.1287/mnsc.2019.3550}
Chu, J., Y. Duan, X. Yang, and L. Wang. 2021. The Last Mile Matters: Impact of Dockless Bike Sharing on Subway Housing Price Premium. \textit{Management Science}, 67(1), 297-316.

@@

\bibitem[Li et al.(2019)]{LI2019165}
Li, H., Y. D. Wei, Y. Wu, and G. Tian. 2019. Analyzing Housing Prices in Shanghai with Open Data: Amenity, Accessibility, and Urban Structure. \textit{Cities}, 91, 165-179.

@@
